---
title: "TSC_processing"
output:
  html_document:
    fig_height: 6
    fig_width: 6
    number_sections: yes
    toc: yes
    toc_float: yes
  html_notebook: default
editor_options: 
  chunk_output_type: console
---
## document set up
This is the surface proteomics data analysis for TSC project with Mike Evans group
Charles Trulliet, Loc Huynh, and Junnian Wei
```{r setup}
knitr::opts_knit$set(root.dir = "~/Box Sync/MS/MSpeaklist/TSC_v2/")
knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE,
    fig.align='center',
    fig.pos='H',
    fig.path = "TSC.plots.AND.8/",
    dev = c("png", "pdf"),
    dpi=500
)
```


```{r load data}
load("~/Box Sync/MS/MSpeaklist/TSC_v2/TSC_basal_data_AND_8_original.RData")
source("~/Box Sync/MS/MSpeaklist/codes/SILAC_v2.R")

```


```{r statistics}
print(paste("TSC1 peptides",nrow(skypep[skypep$fil == T & skypep$exp_ref == 'TSC1',])))
print(paste("TSC1 proteins", nrow(skypro[skypro$exp_ref == 'TSC1',])))
print(paste("ID's log2 >2, p val <0.05 =", nrow(skypro[skypro$exp_ref == 'TSC1' & skypro$enrich.exp.med > 2 & skypro$enrich.exp.p > -log10(0.05),])))

```

```{r volcano}
Volplot(skypro, r.cutoff = 2)
`skypro-TSC1-graph`+ ylim(0,13) + xlim(0,6) 

# Volplot(skypro, r.cutoff = 1, custom = "Anpep|Mme|Tfrc|", customlab = "custom")
flow <- t(read.csv("~/Box Sync/MS/MSpeaklist/TSC_v2/flowlist.csv", stringsAsFactors = F, header = F))
Volplot(skypro, custom = as.character(flow), customlab = "custom", r.cutoff = 2)

sig.hit <- skypro[skypro$enrich.exp.p > 1.3 & grepl("TSC1", skypro$exp_ref), ]
top.hit <- NULL
top.hit <- sig.hit[c(head(order(-sig.hit$enrich.exp.med), n=16), tail(order(-sig.hit$enrich.exp.med), n=10)), "Protein.Gene"]

top.hit <- sig.hit[c(head(order(-sig.hit$enrich.exp.med), n=20)), "Protein.Gene"]

Volplot(skypro, custom = c(as.character(top.hit),"Slc2a1"), customlab = "custom", r.cutoff = 2)

`skypro-TSC1-graph`+ ylim(0,13) + xlim(-6,6) + scale_x_continuous(breaks=c(seq(-6,6,2)))
`skypro-TSC1-graph`+ scale_x_continuous(breaks=c(0,1,2,3,4,5,6)) + scale_y_continuous(breaks=c(seq(0,12,2))) + coord_cartesian(ylim = c(0,12),  xlim = c(0,5.5))

g <- `skypro-TSC1-graph` + xlim(-1,5.5)

g + scale_x_continuous(breaks=c(0,1,2,3,4,5,6)) + scale_y_continuous(breaks=c(seq(0,12,2))) + coord_cartesian(ylim = c(0,12),  xlim = c(0,5.5))+ xlim(-1,5.5)

flow_MS <- skypro[skypro$Protein.Gene %in% flow & grepl("TSC1", skypro$exp_ref),]

flow_MS$pvalue <- 10^-flow_MS$enrich.exp.p
flow_MS$order <- factor(flow_MS$Protein.Gene,levels=flow)
flow_MS <- flow_MS[order(flow_MS$order),]

top_MS <- skypro[grepl("TSC1", skypro$exp_ref) & skypro$enrich.exp.p > -log10(0.05),]
top_MS <- top_MS[order(-top_MS$enrich.exp.med),]
head(top_MS,20)

# write.csv(head(top_MS,20),"~/Box Sync/MS/MSpeaklist/TSC_v2/target_top20.csv")
# write.csv(flow_MS,"~/Box Sync/MS/MSpeaklist/TSC_v2/flow_target_top20_paper.csv")
# write.csv(skypro, "~/Box Sync/MS/MSpeaklist/TSC_v2/TSC_v2_03102018_AND_data.csv")
# load("~/Box Sync/MS/MSpeaklist/TSC_v2/TSC_basal_data_OR_8_proc2.RData")
# write.csv(skypro, "~/Box Sync/MS/MSpeaklist/TSC_v2/TSC_v2_03102018_OR_data.csv")

# write.csv(skypro[skypro$exp_ref == 'TSC1',], "~/Box Sync/MS/MSpeaklist/TSC_v2/TSC1_v2_06212108_AND_data_deposit.csv")
```

```{r log2 dist}
log2dist(skypep)
log2dist(skypep[skypep$exp_ref == 'TSC1',])

```


```{r SILAC comparison}
HLpro(skypep[skypep$fil == T,])
library(reshape2)
SILAC_comp <- dcast(skypro_ind, Protein.Accession + Protein.Gene ~ raw_id, value.var = "enrich.rep.med")
SILAC_comp$TSC1_diff <- (SILAC_comp$`Q20160916-04.raw`-SILAC_comp$`Q20160916-02.raw`)^2

```
## TSC1 vs TSC2 dataset

### venn diagram of ID
```{r ID venn overlap} 
library(limma)
ID_comp <- dcast(skypro, Protein.Accession + Protein.Gene ~ exp_ref, value.var = "enrich.exp.p")

vennDiagram(apply(ID_comp[3:4], 2, function(x) ifelse(!is.na(x), 1, 0)), include = c("up"), counts.col = c("red"), main = paste("all IDs n=",nrow(ID_comp)))

vennDiagram(apply(ID_comp[3:4], 2, function(x) ifelse(x < -log10(0.05) , 1, 0)), include = c("up"), counts.col = c("red"), main = paste("sig overlap IDs n=",nrow(ID_comp),"- bottom right number"))

```


###Scatter plot of proteins identified in both TSC1 vs TSC2 dataset, p value < 0.05 (n=138 ID in both)
```{r TSC1 vs TSC2}
library(reshape2)
library(ggrepel)
#subset sig proteins
compare <- dcast(skypro[skypro$enrich.exp.p > -log10(0.05),], Protein.Accession + Protein.Gene ~ exp_ref, value.var = "enrich.exp.med")
p <- ggplot(compare, aes(TSC1, TSC2)) + geom_jitter(color = "grey") + theme_classic()
p + geom_text_repel(data = compare[compare$TSC1 > 1 & compare$TSC2 > 1,], aes(label = Protein.Gene), nudge_x = 0.25, nudge_y = 0.25) + geom_text_repel(data = compare[compare$TSC1 < -1 & compare$TSC2 < -1,], aes(label = Protein.Gene), nudge_x = -0.25, nudge_y = -0.25) + ggtitle(paste("sig overlapping IDs",nrow(compare)))

p + geom_text_repel(data = compare[grepl("Tf", compare$Protein.Gene),], aes(label = Protein.Gene), fontface = "bold")
p + geom_text_repel(data = compare[grepl("Mme|Tfrc|Anpep|Slc2a1", compare$Protein.Gene),], aes(label = Protein.Gene), fontface = "bold") + geom_point(data = compare[grepl("Mme|Tfrc|Anpep|Slc2a1", compare$Protein.Gene),], aes(color = "yellow")) +theme(legend.position="none") + geom_vline(xintercept = c(-1,0,1), color = c("grey", "black", "grey")) +geom_hline(yintercept = c(-1,0,1), color = c("grey", "black", "grey"))

```

```{r venn diagram TSC1vsTSC2}
library(limma)
vennDiagram(apply(compare[3:4], 2, function(x) ifelse(!is.na(x), 1, 0)), include = c("up"), counts.col = c("red"), main = "all IDs (n=612)")
vennDiagram(apply(compare[3:4], 2, function(x) ifelse(x > 1, 1, ifelse(x < -1, -1, 0))), include = c("up","down"), counts.col = c("red","green"), main = "differential regulation (FC > 2, p value < 0.05) (n=263)")

```

```{r vol overlap}
common_updown <- apply(apply(compare[3:4], 2, function(x) ifelse(x > 1, 1, ifelse(x < -1, -1, 0))),1, sum, na.rm=TRUE)
compare[common_updown > 1 | common_updown < -1, ]
custom <- as.character(compare[common_updown > 1 | common_updown < -1, "Protein.Gene"])

Volplot(skypro, r.cutoff = 1, custom = custom, customlab = "custom")
```



```{r volcano label}
Volplot(skypro, r.cutoff = 1, custom = c("Tfrc","Slc2a1","Mme","Anpep"), customlab = "custom")
library(ggplot2)


```

```{r top hits TSC1, fig.height=8, fig.width=6}
tsc1 <- skypro[grepl("TSC1", skypro$exp_ref) & skypro$enrich.exp.p > 1.3 & skypro$enrich.exp.med > 1,]
tsc1.1 <- tsc1[rev(order(tsc1$enrich.exp.med)),c(2,4,5)]
# write.csv(tsc1.1, "./tsc1_top_OR.csv")

library(RColorBrewer)
library(GMD)

col.heat <- colorRampPalette(brewer.pal(8,"Blues"))
heatmap.3(tsc1.1[2:3], labRow = as.character(tsc1.1$Protein.Gene), dendrogram = "none", color.FUN = col.heat, breaks = c(seq(0,4,0.1)),  cluster.by.Row = F, cluster.by.Col = T, Colv = F, Rowv = F)


```
## GSEA
```{r GSEA, fig.height = 6, fig.width=14}
load("~/Box Sync/MS/MSpeaklist/MySigDB/mouse_c5_v5p2.rdata")
library(UniProt.ws)
library(fgsea)
source("~/Box Sync/MS/MSpeaklist/codes/fgsea_plot_enrichment_KL.R")
# library(reactome.db)

skypro.TSC1 <- skypro[skypro$exp_ref == 'TSC1',]
# 
# mouse <- UniProt.ws(taxId=10090)
# save(mouse, file = "~/Box Sync/MS/MSpeaklist/MySigDB/mouse.Rdata")
load("~/Box Sync/MS/MSpeaklist/MySigDB/mouse.Rdata")
# 
test <- select(mouse, unique(skypro.TSC1$Protein.Accession), columns = "ENTREZ_GENE")
test2 <- skypro.TSC1[skypro.TSC1$Protein.Accession %in% test$UNIPROTKB,]

colnames(test)[1] <- "Protein.Accession"
pro.matrix <- merge(test, test2, by = "Protein.Accession")

pro.stat <- pro.matrix[order(-pro.matrix$enrich.exp.med),"enrich.exp.med"]
names(pro.stat) <-  pro.matrix[order(-pro.matrix$enrich.exp.med),"ENTREZ_GENE"]
gsea_out <- fgsea(pathways=Mm.c5, stats=pro.stat,  minSize=15, maxSize=500, nperm=100000)

topPathways <- gsea_out[head(order(pval), n=15)][order(NES), pathway]
# topPathways.up <- gsea_out[head(order(-NES), n=15)][,pathway]

topPathways.up <- gsea_out[ES > 0][head(order(pval), n=15), pathway]
topPathways.down <- gsea_out[ES < 0][head(order(pval), n=15), pathway]
#TOP table
plotGseaTable(Mm.c5[topPathways], pro.stat, gsea_out, gseaParam=0.5)
plotGseaTable(Mm.c5[topPathways.up], pro.stat, gsea_out, gseaParam=0.5)
plotGseaTable(Mm.c5[topPathways.down], pro.stat, gsea_out, gseaParam=0.5)

```

```{r GSEA GO up}
for (i in 1:length(topPathways.up)){
  print(paste(topPathways.up[i]))
  plotEnrichment_KL(Mm.c5[[topPathways.up[i]]], pro.stat)
  Volplot(skypro.TSC1, custom = pro.matrix[pro.matrix$ENTREZ_GENE %in% unlist(gsea_out[grepl(topPathways.up[i], gsea_out$pathway), leadingEdge]),3], customlab = "custom")
}

```

``` {r GSEA GO down}
for (i in 1:length(topPathways.down)){
  print(paste(topPathways.down[i]))
  plotEnrichment_KL(Mm.c5[[topPathways.down[i]]], pro.stat)
  Volplot(skypro.TSC1, custom = pro.matrix[pro.matrix$ENTREZ_GENE %in% unlist(gsea_out[grepl(topPathways.down[i], gsea_out$pathway), leadingEdge]),3], customlab = "custom")
}


```

```{r repeat with KEGG,fig.height = 6, fig.width=14}
load("~/Box Sync/MS/MSpeaklist/MySigDB/mouse_c2_v5p2.rdata")
load("~/Box Sync/MS/MSpeaklist/MySigDB/mouse_H_v5p2.rdata")
Mm.c2_KR <- Mm.c2[grepl("BIOCARTA|KEGG|REACTOME", names(Mm.c2))]
Mm.KL <- c(Mm.c2_KR, Mm.H)

gsea_out <- fgsea(pathways=Mm.KL, stats=pro.stat,  minSize=15, maxSize=500, nperm=100000)

topPathways <- gsea_out[head(order(pval), n=15),pathway]
# topPathways.up <- gsea_out[head(order(-NES), n=15)][,pathway]

topPathways.up <- gsea_out[ES > 0][head(order(pval), n=15), pathway]
topPathways.down <- gsea_out[ES < 0][head(order(pval), n=15), pathway]
#TOP table
plotGseaTable(Mm.KL[topPathways], pro.stat, gsea_out, gseaParam=0.5)
#top upregulated
plotGseaTable(Mm.KL[topPathways.up], pro.stat, gsea_out, gseaParam=0.5)

#top down
plotGseaTable(Mm.KL[topPathways.down], pro.stat, gsea_out, gseaParam=0.5)

#top leading edge pathways


```

```{r GSEA KEGG up }
for (i in 1:length(topPathways.up)){
  print(paste(topPathways.up[i]))
  plotEnrichment_KL(Mm.KL[[topPathways.up[i]]], pro.stat)
  Volplot(skypro.TSC1, custom = pro.matrix[pro.matrix$ENTREZ_GENE %in% unlist(gsea_out[grepl(topPathways.up[i], gsea_out$pathway), leadingEdge]),3], customlab = "custom")
}

```


```{r GSEA KEGG down}
for (i in 1:length(topPathways.down)){
  print(paste(topPathways.down[i]))
  plotEnrichment_KL(Mm.KL[[topPathways.down[i]]], pro.stat)
  Volplot(skypro.TSC1, custom = pro.matrix[pro.matrix$ENTREZ_GENE %in% unlist(gsea_out[grepl(topPathways.down[i], gsea_out$pathway), leadingEdge]),3], customlab = "custom")
}


print(pro.matrix[pro.matrix$ENTREZ_GENE %in% unlist(gsea_out[grepl(topPathways.down[1], gsea_out$pathway), leadingEdge]),3])
```


#GSEA with 3+ pep
```{r GSEA repeat with 3 or more peptides, fig.height = 6, fig.width=12}
skypro.TSC1 <- skypro[skypro$exp_ref == 'TSC1' & skypro$enrich.exp.count > 2,]
# 
# mouse <- UniProt.ws(taxId=10090)
# 
test <- select(mouse, unique(skypro.TSC1$Protein.Accession), columns = "ENTREZ_GENE")
test2 <- skypro.TSC1[skypro.TSC1$Protein.Accession %in% test$UNIPROTKB,]

colnames(test)[1] <- "Protein.Accession"
pro.matrix <- merge(test, test2, by = "Protein.Accession")

pro.stat <- pro.matrix[order(-pro.matrix$enrich.exp.med),"enrich.exp.med"]
names(pro.stat) <-  pro.matrix[order(-pro.matrix$enrich.exp.med),"ENTREZ_GENE"]
gsea_out <- fgsea(pathways=Mm.c5, stats=pro.stat,  minSize=15, maxSize=500, nperm=100000)

topPathways <- gsea_out[head(order(pval), n=15)][order(NES), pathway]
# topPathways.up <- gsea_out[head(order(-NES), n=15)][,pathway]

topPathways.up <- gsea_out[ES > 0][head(order(pval), n=15), pathway]
topPathways.down <- gsea_out[ES < 0][head(order(pval), n=15), pathway]
#TOP table
plotGseaTable(Mm.c5[topPathways], pro.stat, gsea_out, gseaParam=0.5)
#top upregulated
plotGseaTable(Mm.c5[topPathways.up], pro.stat, gsea_out, gseaParam=0.5)
#top down
plotGseaTable(Mm.c5[topPathways.down], pro.stat, gsea_out, gseaParam=0.5)

#top leading edge pathways

for (i in 1:length(topPathways.up)){
  print(paste(topPathways.up[i]))
  plotEnrichment_KL(Mm.c5[[topPathways.up[i]]], pro.stat)
  Volplot(skypro.TSC1, custom = pro.matrix[pro.matrix$ENTREZ_GENE %in% unlist(gsea_out[grepl(topPathways.up[i], gsea_out$pathway), leadingEdge]),3], customlab = "custom")
}
for (i in 1:length(topPathways.down)){
  print(paste(topPathways.up[i]))
  plotEnrichment_KL(Mm.c5[[topPathways.up[i]]], pro.stat)
  Volplot(skypro.TSC1, custom = pro.matrix[pro.matrix$ENTREZ_GENE %in% unlist(gsea_out[grepl(topPathways.up[i], gsea_out$pathway), leadingEdge]),3], customlab = "custom")
}


```

```{r repeat GSEA 3 plus peptide with HALLMARK KEGG REACTOME BIOCARTA, fig.height = 6, fig.width=10}
# load("~/Box Sync/MS/MSpeaklist/MySigDB/mouse_c2_v5p2.rdata")
# load("~/Box Sync/MS/MSpeaklist/MySigDB/mouse_H_v5p2.rdata")
# Mm.c2_KR <- Mm.c2[grepl("BIOCARTA|KEGG|REACTOME", names(Mm.c2))]
Mm.KL <- c(Mm.c2_KR, Mm.H)

gsea_out <- fgsea(pathways=Mm.KL, stats=pro.stat,  minSize=15, maxSize=500, nperm=100000)

topPathways <- gsea_out[head(order(pval), n=15),pathway]
# topPathways.up <- gsea_out[head(order(-NES), n=15)][,pathway]

topPathways.up <- gsea_out[ES > 0][head(order(pval), n=15), pathway]
topPathways.down <- gsea_out[ES < 0][head(order(pval), n=15), pathway]
#TOP table
plotGseaTable(Mm.KL[topPathways], pro.stat, gsea_out, gseaParam=0.5)
#top upregulated
plotGseaTable(Mm.KL[topPathways.up], pro.stat, gsea_out, gseaParam=0.5)

#top down
plotGseaTable(Mm.KL[topPathways.down], pro.stat, gsea_out, gseaParam=0.5)

#top leading edge pathways

for (i in 1:length(topPathways.up)){
  print(paste(topPathways.up[i]))
  plotEnrichment_KL(Mm.KL[[topPathways.up[i]]], pro.stat)
  Volplot(skypro.TSC1, custom = pro.matrix[pro.matrix$ENTREZ_GENE %in% unlist(gsea_out[grepl(topPathways.up[i], gsea_out$pathway), leadingEdge]),3], customlab = "custom")
}

for (i in 1:length(topPathways.down)){
  print(paste(topPathways.down[i]))
  plotEnrichment_KL(Mm.KL[[topPathways.down[i]]], pro.stat)
  Volplot(skypro.TSC1, custom = pro.matrix[pro.matrix$ENTREZ_GENE %in% unlist(gsea_out[grepl(topPathways.down[i], gsea_out$pathway), leadingEdge]),3], customlab = "custom")
}

# for (i in 1:length(topPathways)){
#   print(paste(topPathways[i]))
#   plotEnrichment_KL(Mm.KL[[topPathways[i]]], pro.stat)
#   Volplot(skypro.TSC1, custom = pro.matrix[pro.matrix$ENTREZ_GENE %in% unlist(gsea_out[grepl(topPathways[i], gsea_out$pathway), leadingEdge]),3], customlab = "custom")
# }

```



